Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-18 ICLR25/formula.tex
update formula.tex

For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative. Next we consider the following definition.

>>>>

For nodes $c$ in the layer between $a$ and $b$, according to the LP solution, we may check $v(c)$ is positive or negative, that will be the following definition.
